---
title: "Wirtschaftlichkeit Saisonaler Erdwärmespeicher"
format: gfm
editor: source
---

## Setup

```{r}
# RStudio 23.12.0 on Linux Mint Debian Edition 6
# install python version = '3' #3.12
# install.packages('reticulate')
library(reticulate)
# reticulate::repl_python() #say yes
# py_install("pandas", envname = 'r-reticulate')
# py_install("openpyxl", envname = 'r-reticulate')
# py_install(c('matplotlib', 'seaborn'), envname = 'r-reticulate')

```

## Language

Choice of language: As this work is based on heliogaia.de which is written in German and as I hope, that a pilot project for "Saisonale Erwärmespeicher" will be started in Germany and thus has to use quite a lot of German data sources and variable names, I am using mostly the German language here.

Sprachwahl: Da diese Arbeit auf heliogaia.de basiert und da ich hoffe, dass ein Pilotprojekt für Saisonale Wärmespeicher in Deutschland realisert wird, also viele deutsche Variablennamen verwenden wird, die auch zur Zeit noch im Entstehen sein sollten, verwende ich hier zunächst der Schnelligkeit halber die deutsche Sprache.

## Start

```{python}
import pandas as pd
#version from 2024-01-11
df = pd.read_excel('/home/danielwittig/repos/Saisonale_Erdwaermespeicher/_base/jahreslauf_roebel.xlsx', sheet_name='e', header = 1)
print(df.shape)
mypyvar0 = df.shape[0]
mypyvar1 = df.shape[1]
df.head(7)
df.loc[:732,'Tag'].hist()
```
```{r}
myrvar= 1
```



## Running Code

* now let's include a python variable here: `r py$mypyvar0` - wow, so inline!
* now let's include an r variable here: `r myrvar` - wow, so inline again! 

When you click the **Render** button a document will be generated that includes both content and the output of embedded code. You can embed code like this:

```{r}
1 + 1
```

You can add options to executable code like this

```{r}
#| echo: false
2 * 2
```

The `echo: false` option disables the printing of code (only output is displayed).
